Water Management

### 2020-01-16 Paper/paper.tex
change style of subsection to arabic numbers
set TeX spellchecker to US english
draft for results section

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------

@@

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

@@

	\section{Conclusion}
	\blindtext

>>>>

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------
% !TeX spellcheck = en_US

@@

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

@@

	\section{Conclusion}
	This chapter will discuss the outcomes and results of the implemented functionality in MATLAB.
	The discussion will be started on the basic questions asked by the project description.
	Furthermore we made several modifications to the task which will be discussed additionally.
	All results will be visualized by plots made within our simulation in MATLAB.
	\subsection{Optimal irrigation policy}
	\subsection{Steady State}
	\subsection{Steady State Probability}
	\subsection{Effect of Changed Discount Factors to Optimal Irrigation Policy}
	\subsection{Changed Volatility of Rainfalls}
